Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
induced text table fix
latest for Josh

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL while
  jointly training a neural network to efficiently search for programs
  in the learned DSL.  We use our model to synthesize functions on lists,
  edit strings, and solve symbolic regression problems, showing how the
  model learns a domain-specific library of program components for
  expressing solutions to problems in the domain.
\end{abstract}

@@

\begin{table}[b]
\centering  \begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (a b) (foldr b (cons "," a)}\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}\\
      \code{($\lambda$ (a b) (foldr a b }\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}
    \end{tabular}&
    \begin{tabular}{l}
      \code{(foldr a b ($\lambda$ (x z) }\\
      \phantom{\code{(foldr a b }}\code{(cons x z)))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x '-') ',' x))) s)}
      \end{tabular}
\\\bottomrule\\
  \end{tabular}
  \caption{The DSL induction algorithm proposes fragments of programs to add to the DSL.
    These fragments are taken from programs in the frontiers (left column). Here, the proposed subexpression (top) appends two lists or (bottom) performs character substitutions.} 
  \label{fragmentExample}
\end{table}

@@

We compare  with four baselines on  held-out tasks:
\\\noindent \textbf{Ours (no NN)}, which lesions the recognition model.
\\\noindent \textbf{RF/DC}, which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a recognition model only from samples from the fixed generative model.
This is equivalent to our algorithm with $\lambda = \infty$ (Sec.~\ref{grammarInductionSection})
and $\mathcal{L}_{\text{RM}} = \mathcal{L}_{\text{HM}}$ (Sec.~\ref{recognitionSection}).
We call this baseline RF/DC because
this setup is closest to how RobustFill~\cite{devlin2017robustfill} and DeepCoder~\cite{balog2016deepcoder} are trained.
We can not compare directly with these systems,
because they are engineered for one specific domain, and 
do not have publicly available code and datasets.
\\\noindent \textbf{EC}, which lesions the recognition model and modifies  the DSL learner to model the library learning technique of  EC~\cite{Dechter:2013:BLV:2540128.2540316}.
\\\noindent \textbf{Enum}, which enumerates a frontier without any learning -- equivalently, our first search step.

>>>>

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL while
  jointly training a neural network to efficiently search for programs
  in the learned DSL.  We use our model to synthesize functions on lists,
  edit text, and solve symbolic regression problems, showing how the
  model learns a domain-specific library of program components for
  expressing solutions to problems in the domain.
\end{abstract}

@@

\begin{table}[b]
\centering  \begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (a b) (foldr b (cons "," a)}\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}\\
      \code{($\lambda$ (a b) (foldr a b }\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}
    \end{tabular}&
    \begin{tabular}{l}
      \code{(foldr a b ($\lambda$ (x z) }\\
      \phantom{\code{(foldr a b }}\code{(cons x z)))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x a) b x))) s)}
      \end{tabular}
\\\bottomrule\\
  \end{tabular}
  \caption{The DSL induction algorithm proposes fragments of programs to add to the DSL.
    These fragments are taken from programs in the frontiers (left column). Here, the proposed subexpression (top) appends two lists or (bottom) performs character substitutions.} 
  \label{fragmentExample}
\end{table}

@@

We compare with ablations of our model on held out tasks.
Each of these ablations is chosen to approximate
a prior approach in the program learning literature:
\\\noindent \textbf{Ours (no NN)}, which lesions the recognition model.
\\\noindent \textbf{RF/DC}, which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a recognition model only from samples from the fixed generative model.
This is equivalent to our algorithm with $\lambda = \infty$ (Sec.~\ref{grammarInductionSection})
and $\mathcal{L}_{\text{RM}} = \mathcal{L}_{\text{HM}}$ (Sec.~\ref{recognitionSection}).
We call this baseline RF/DC because
this setup is closest to how RobustFill~\cite{devlin2017robustfill} and DeepCoder~\cite{balog2016deepcoder} are trained.
We can not compare directly with these systems,
because they are engineered for one specific domain, and 
do not have publicly available code and datasets.
\\\noindent \textbf{EC}, which lesions the recognition model and modifies  the DSL learner to model the library learning technique of  EC~\cite{Dechter:2013:BLV:2540128.2540316}.
\\\noindent \textbf{Enum}, which enumerates a frontier without any learning -- equivalently, our first search step.
